---
title: "Westpoint Cleaning"
author: "Samuel W. Suk"
date: '2022-04-22'
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(knitr.duplicate.label = "allow")
```

##Libraries
```{r, include=FALSE}
library(ggplot2)
library(dplyr)
library(vtable)
library(tidyverse)
library(jtools)
library(fixest)
library(rdrobust)
library(margins)
library(GGally)
library(forcats)
library(lubridate)
library(tibble )
```

##Step 1
Task is to clean and mutate the following West Point USMA data
```{r, echo = TRUE}
westpoint <- read.csv("Westpoint.csv")

westpoint <-westpoint %>%
  rename(year = ï..year)

summary(westpoint)
```

##Step 2
Recreating femalepeers, malespeers, and totpeople columns based on the documentation for each column

```{r, echo=TRUE}
#recreating malespeers
westpoint2 <- westpoint %>%
  group_by(company_n, class, year) %>%
  mutate(malespeers2 = sum(1-female)- (1-female))

#recreating femalespeers
westpoint2 <- westpoint2 %>%
  group_by(company_n, class, year) %>%
  mutate(femalespeers2 = sum(female)- (female))

#recreating totpeoples
westpoint2 <- westpoint2 %>%
  mutate(totpeople2 = malespeers2 + femalespeers2)

#New columns
westpoint2

```

##Step 3
Investigate the rows for which your recreation "doesn't" line up exactly. Any ideas what the issue might be? Do you trust the original or your recreation more?

  The recreation varies from the original model because it is not including myself, nor the column of people who are graduating or            continuing elsewhere. Depending on what I want to evaluate, with or without graduates, the trust is equal. 


##Step 4
Create two new columns from company_n: company, and division
```{r, echo= TRUE}
westpoint2$company = substr(westpoint2$company_n, 1, 1)
westpoint2$division = substr(westpoint2$company_n, 3,3)
westpoint2

```

##Step 5
Limit data to years in which we have all four cohorts present in full quantity. 
```{r, echo= TRUE}
westpointfull <- westpoint2 %>%
  filter(year > 80,
         year < 82)
```

##Step 6a
 Top four companies (A, B, C, etc., not A-1, A-2) with the highest continue_or_grad rates
```{r, echo= TRUE}
top4compgradrate <- westpointfull %>%
  group_by(company) %>%
  summarise(gradrate = mean(continue_or_grad)) %>%
  arrange(gradrate) %>%
slice(9:6)
top4compgradrate
```

##Step 6b
continue_or_grad rates by class 
```{r, echo = TRUE}
top4classgradrate <- westpointfull %>%
  group_by(class) %>%
  summarise(gradrate = mean(continue_or_grad)) %>%
  arrange(-gradrate)
top4classgradrate
```

##Step 6c
continue_or_grad rates of women by class
```{r, echo= TRUE}
femalegradrate <- westpointfull %>%
  filter(female == 1) %>%
  group_by(female, class) %>%
  summarise(gradrate = mean(continue_or_grad)) %>%
  arrange(-gradrate) 
femalegradrate

```

##Step 7
Bonus task (ungraded): notice anything strange about the "random assignment" of women?

  female peers are randomly assigned by blocks. When ordered by year, there are synchronized stretches of femalepeers from 1 to 2 all the     way to 8

```{r, echo= TRUE}
table(westpoint2$femalespeers)
```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
